Near Optimal Behavior via Approximate State Abstraction

### 2016-05-24 paper/theory_results.tex
../theory_results.tex

By the approximation in Equation~\ref{eq:e_to_x_approx} and the assumption in Equation~\ref{eq:bolt_denom}:
\begin{align*}
\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon}\right| \leq \varepsilon
\label{eq:bolt_with_approx}
\end{align*}
There are two cases of interest - either the $1 + x + \delta$ approximation is maximal or minimal in Equation~\ref{eq:bolt_with_approx}. That is, we either have $\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon$, or $\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon$.

>>>>

By the approximation in Equation~\ref{eq:e_to_x_approx} and the assumption in Equation~\ref{eq:bolt_denom}:
\begin{align}
\left|\frac{1 + Q_G(s_1,a) + \delta_1}{\sum_j e^{Q_G(s_1,a_j)}} - \frac{1 + Q_G(s_2,a) + \delta_2}{\sum_j e^{Q_G(s_1,a_j)} \pm k\varepsilon}\right| \leq \varepsilon \label{eq:bolt_with_approx}
\end{align}
Either the $1 + x + \delta$ approximation is maximal or minimal in Equation~\ref{eq:bolt_with_approx}. That is, either $\sum_j e^{Q_G(s_1,a_j)} + k\varepsilon$, or $\sum_j e^{Q_G(s_1,a_j)} - k\varepsilon$.
